Maenpuen *et al.* --American Journal of Botany-- Appendix S1

### 2022-06-19 ms/response_letter_2.Rmd

---
geometry: margin=1in
link-citations: yes
#csl: templates/xxxx.csl
#bibliography: xxxx.bib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
 # - \linenumbers
output:
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: no
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

Dear Editors,

We hereby resubmit the manuscript (AJB-D-21-00391R1), “Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)” (Phisamai Maenpuen, Masatoshi Katabuchi, Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, Ya-Jun Chen).
We thank the associate editor and the reviewers for their careful attention to detail in our manuscript and for providing comments that have greatly improved the study.

We found small errors in R codes and the total number of individuals used in our analysis was increased from 1365 to 1469.
Accordingly, several statistical values have changed slightly (highlighted in blue).
Additionally, we have cited one more R package that made a significant contribution to workflow management (Line 233-234).

@@

> Line 169 Remove second "using a micrometer".

Thank you.
We have corrected it (Line 170).

> Lines 311-317 I love this inclusion in the revision. However, I'm not clear on the difference between eq. 1 and 2 and between eq. 3 and 4. Please clarify when authors should use each. Also please clarify how generalizable you believe these equations are.

Thank you.
We have added an explnation of the differences, and the text now reads:
"Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions (Warton et al., 2006)" (Line 321-323)

@@

> In the Materials and Methods section please provide the city, spelled-out state (if in USA), and country for the locations and companies mentioned (such as L175).

Confirmed:
We have spelled-out state (Ohio) (Line 176).

> Would you like to thank the reviewers in the acknowledgements? It is not required, but we recommend it, especially if you found their comments helpful. (They don’t, as a rule, see your final response letter.)

Confirmed:
We have added a new line for the acknowledgements (line 379-380).

### 2022-06-19 ms/LMA_method.Rmd
update zenodo

SMA analyses were run as described above.
We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022] using the package targets version 0.12.0 for workflow management [@Landau2021]

@@

Data and codes for this manuscript are archived on Zenodo (XXX) and also available at https://github.com/mattocci27/leaf-disc.

>>>>

SMA analyses were run as described above.
We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022] using the R package *targets* version 0.12.0 for workflow management [@Landau2021]

@@

Data and codes for this manuscript are archived on Zenodo at https://doi.org/10.5281/zenodo.6665083 and also available on Github at https://github.com/mattocci27/leaf-disc.

### 2022-06-19 ms/LMA_method.tex
update zenodo

SMA analyses were run as described above.
We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}) using the package targets version 0.12.0 for workflow management (\protect\hyperlink{ref-Landau2021}{Landau, 2021})

@@

Data and codes for this manuscript are archived on Zenodo (XXX) and also available at \url{https://github.com/mattocci27/leaf-disc}.

>>>>

SMA analyses were run as described above.
We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}) using the R package \emph{targets} version 0.12.0 for workflow management (\protect\hyperlink{ref-Landau2021}{Landau, 2021})

@@

Data and codes for this manuscript are archived on Zenodo at \url{https://doi.org/10.5281/zenodo.6665083} and also available on Github at \url{https://github.com/mattocci27/leaf-disc}.
